%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% Collaborators : Santiago Aguilera
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemItalic}[3]{
  \item\small{
    \textbf{#1 (\textit{#2})}{: #3 \vspace{-2pt}}
  }\vspace{-4pt}
}

\newcommand{\resumeItemAlign}[2]{
  \vspace{-1pt}\item\small{
    \textbf{#1} \hfill \textit{#2}
  }\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{{\Large Santiago Aguilera}}
\end{center}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  DNI. 37786146 & Email : \href{mailto:aguilerasanti@hotmail.com}{aguilerasanti@hotmail.com}\\
  Rodriguez Peña 2731, Martinez, Buenos Aires & Mobile : (+54) 9 11 6171 7736 \\
  1993/08/26 & LinkedIn: \href{https://www.linkedin.com/in/santiaguilera/}{/in/santiaguilera/}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Facultad de Ingeniería, Universidad de Buenos Aires}{Buenos Aires}
    {Informatic Engineering}{Present}
  \resumeSubheading
    {Colegio Carmen Arriola de Marín}{Buenos Aires}
    {Goods and Services Production Bachelor}{2011}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Mercado Libre SRL}{Buenos Aires}
    {Ssr. Software Engineer}{Jun 2016 - Present}
    \resumeItemListStart
      \resumeItem{Architecture}
       {Mobile Architecture team. Development of iOS/Android/Backend applications and libraries.}
      \resumeItem{Build Tools}
        {Created a gradle plugin providing SCA, lints, archives upload, easier tools for development, dynamic dependency management, coverage support, unit-testing configurations, etc.}
      \resumeItem{Size}
        {Created libraries and services for reducing the applications size (eg. Android .apk was decreased from 30 MB to 9 MB). This process included getting resources on-demand, .arsc optimization (for Android), stronger minifier optimizations, WebP support, bytecode optimizations, among others.}
      \resumeItem{Security}
        {Analyzed and fixed critical and mid-level security issues in the applications.}
      \resumeItem{CI}
        {Created a highly scalable and efficient framework for CI services, with built-in webhooks to make code analysis, build analysis, testing, deploying, distributing, etc.}
      \resumeItem{Technologies}
        {Strong usage of Java, Obj-C, Groovy, Ruby, C++, Bash, Kotlin, Python, Node.js, Gradle, NDK, Cocoa, Tomcat, Jetty, Docker, Nginx, Danger, Calabash, Fastlane, ASM, Cucumber, Proguard, etc.}
  \resumeItemListEnd

  \resumeSubheading
    {Amalgama Software}{Buenos Aires}
    {Sr. Android Developer}{Dec 2014 - Jun 2016}

  \resumeSubheading
    {FI.UBA}{Buenos Aires}
    {Algorithms II Assistant Professor}{Mar 2013 - Dec 2013}

  \resumeSubheading
    {Febicom SA}{Buenos Aires}
    {Technical Hardware Internship}{Apr 2011 - Jun 2011}

  \resumeSubheading
    {Myself}{Buenos Aires}
    {Private School Tutoring}{Nov 2009 - Nov 2014}

\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects (more available at www.github.com/saantiaguilera)}
\resumeSubHeadingListStart
  \resumeItemItalic{SecureKeys}{Java, Groovy, NDK}
    {Android library for storing information locally in a safer way}
  \resumeItemItalic{Gossip Protocol}{Kotlin}
    {Gossip Protocol implementation in kotlin for failure detection, monitoring, etc.}
  \resumeItemItalic{RxFacebook}{Kotlin}
    {Fully customizable reactive extension for the Facebook SDK}
  \resumeItemItalic{Tallerify}{C++, Node.js, AngularJS, Java}
    {Shared \& web server, admin panel and android app for a "Spotify".}
  \resumeItemItalic{Disney Emoji Keyboard}{Java, NDK}
    {Android custom system keyboard that also provides Gifs/Images/Emojis}
  \resumeItemItalic{Global Codecov}{Ruby}
    {Gem for triggering codecov coverage tool, supporting any language.}
  \resumeItemItalic{AgentBot}{Java, NDK}
    {Android application with voice recognition for E-Commerce purposes.}
  \resumeItemItalic{Loquacious}{Kotlin}
    {Localized remote resource manager library for Android.}
\resumeSubHeadingListEnd


%--------LANGUAGES------------
\section{Languages}
\resumeSubHeadingListStart
  \resumeSubItem{Highly profficient}
    {Java, Kotlin, Groovy, Shell, Ruby}
  \resumeSubItem{Profficient}
    {C++, C, Swift, Node.js, Python, Javascript}
  \resumeSubItem{Knowledgeable}
    {Clojure, Lisp, Smalltalk, Scala, Obj-C, MIPS Assembly, SQL, Perl}
\resumeSubHeadingListEnd

%--------ACHIEVEMENTS------------
\section{Achievements}
\resumeSubHeadingListStart
  \resumeItemAlign{IGCSE Extended \& ICE English Cambridge Certificates}{Dec 2010}
  \resumeItemAlign{Top 100/2500 in Kaggle Big Data Competition (/sf-crime)}{Jun 2016}
  \resumeItemAlign{Ranked in the top 10\% of MercadoLibre developers}{2016}
  \resumeItemAlign{Deeplearning.ai Coursera Specialization}{Sep 2017}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
